---
output: github_document
---

目前没有欺诈的标签，先按照无监督学习做一次看看。

1. 一般无时间纬度，查看箱型图
1. 有时间纬度，查看是否产生一小段连续异常值

先从认识数据开始，把这些图总结出来。

```{r setup,message=FALSE, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(data.table)
library(tidyverse)
```

```{r}
river <- fread('data/river.csv',drop = 'V1')
```

```{r}
# Explore contents of dataset
head(river)

# Summary statistics of river nitrate concentrations
summary(river$nitrate)

# Plot the distribution of nitrate concentration
boxplot(river$nitrate)
```

<input type="checkbox" id="checkbox1" class="styled">省份数据找下经纬度进行处理

# Grubbs' test

>
Before using Grubbs' test, you should first check that the observations are plausibly normal. 

先检验是否符合正太分布，否则不能用 Grubbs 检验

```{r}
# Separate the histogram into 40 bins 
hist(river$nitrate, xlab = "Nitrate concentration", breaks = 40)
```

>
Grubbs' test assesses whether the value that is farthest from the mean is an outlier.

```{r}
library(outliers)
grubbs.test(river$nitrate)
```

因此判断
highest value 1.897 is an outlier
为异常值

因此剔除这个值，进行 while loop 直到 p 值在0.05水平之上

<input type="checkbox" id="checkbox1" class="styled">`grubbs.test` 的 while loop

# Seasonal-Hybrid ESD algorithm

时间序列的异常值检测，参考
twitter 的 R包 AnomalyDetection。

>
Spot on! Grubbs' test can only take an extreme value as a candidate for an outlier, while Seasonal-Hybrid ESD explicitly accounts for the repeating seasonal patterns. Therefore, it is likely that the extra anomalies have been identified as extreme with respect to the seasonal pattern in the data.

`AnomalyDetectionVec`函数在原来的GitHub 和 R CRAN 已经失效，我进行了封装也不行，因此是该包的结构有问题。
目前的方法是直接录入函数。

<input type="checkbox" id="checkbox1" class="styled">之后我考虑重新写下这个包

```{r eval=F}
list.files('AnomalyDetection_func',full.names = T) %>% 
    map(source)
```

```{r eval=T, message=FALSE, warning=FALSE, include=FALSE}
list.files('AnomalyDetection_func',full.names = T) %>% 
    map(source)
```


```{r}
# Run Seasonal-Hybrid ESD for nitrate concentrations
# Use Seasonal-Hybrid ESD for nitrate concentrations
river_anomalies <- AnomalyDetectionVec(x = river$nitrate, period = 12, direction = 'both', plot = T)

# Print the anomalies
river_anomalies$anoms

# Print the plot
print(river_anomalies$plot)
```

还有更好的选择
，可以关注这些博客

* [Anomaly Detection with Wikipedia Page View Data – Beautiful Data](http://beautifuldata.net/2015/01/anomaly-detection-with-wikipedia-page-view-data/)
